Pre- and Post-Debate Democratic Primary Data: Twitter, Google Trends, and Polls

### 2019-12-11 Paper/paper-draft-Padgett-Thiam.Rmd
put app online

```{r, echo = FALSE, include=FALSE}
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
library(repmis)
library(httr)
library(rsconnect)
library(pander)

@@

all_data$Pre_post <- factor(all_data$Pre_post, levels = c("Pre-debate", 
                                                          "Post-debate"))
```

Then, we created a shiny app, which can be viewed at https://znpadgett.shinyapps.io/shinyapp/:
```{r, eval=FALSE, tidy=TRUE}
# Define UI
surv727app <-
ui <- fluidPage(

@@

```{r, eval=FALSE, include=FALSE}
#upload shiny app to the web - fake secret
rsconnect::setAccountInfo(name='znpadgett',
			  token='DA192A4A3FA4FB169FE8B04D20CA9CEA',
			  secret='XXXXXXXXXXXXXXXXXXXXXXXXXX')
```

>>>>

```{r, echo = FALSE, include=FALSE}
library(knitr)
library(tidyverse)
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggmap)
library(readxl)
library(shiny)
library(rtweet)
library(tidytext)
library(stringr)
library(lubridate)
library(quanteda)
library(SentimentAnalysis)
library(GGally)
library(repmis)
library(httr)
library(pander)
```

@@

all_data$Pre_post <- factor(all_data$Pre_post, levels = c("Pre-debate", 
                                                          "Post-debate"))

Then, we created a shiny app, which can be viewed at https://znpadgett.shinyapps.io/surv727app/:
```{r, eval=FALSE, tidy=TRUE}
# Define UI

ui <- fluidPage(

@@
